Data Preparation, Integration and Cleaning

### 2017-02-17 abbDataPrep_Script.Rmd
outputting figures as rdata

@@

@@

    ggplot(str.data, aes(x=listing.type)) + 
      geom_bar(color=str.col, fill=str.col) +
      xlab('\nListing Type\n') + 
      ggtitle('\nShort Term Rentals by Listing Type\n')  +
      ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

  save(str.types, file=paste0(fig.path, 'strtypes.RData'))
  save(ltr.types, file=paste0(fig.path, 'ltrtypes.RData'))

@@

  list.types <- ggplot(str.data, aes(x=listing.type)) + 
      geom_bar(color=str.col, fill=str.col) +
      xlab('\nListing Type\n') + 
      ggtitle('\nShort Term Rentals by Listing Type\n')  +
      ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

    list.types

@@

  save(list.types, file=paste0(fig.path, 'listtypes.RData'))

@@

  save(ltrbed, file=paste0(fig.path, 'ltrbed.RData'))
  save(strbed, file=paste0(fig.path, 'strbed.RData'))

@@

  save(ltbath, file=paste0(fig.path, 'ltrbath.RData'))
  save(stbath, file=paste0(fig.path, 'strbath.RData'))

@@

  save(ltbb, file=paste0(fig.path, 'ltrbb.RData'))
  save(stbb, file=paste0(fig.path, 'strbb.RData'))

@@

  save(ltr.plot, file=paste0(fig.path, 'rentplot.RData'))
  save(rate.plot, file=paste0(fig.path, 'rateplot.RData'))

@@

  save(loc.map, file=paste0(fig.path, 'suburbMap.RData'))

@@

  save(str.map, file=paste0(fig.path, 'strMap.RData'))
  save(ltr.map, file=paste0(fig.path, 'ltrMap.RData'))

@@

  save(strtype.map, file=paste0(fig.path, 'strsubplot.RData'))
  save(ltrtype.map, file=paste0(fig.path, 'ltrsubplot.RData'))
